---
title: "Model Climatology Quantile/Mean Differences"
output: pdf_document
---

```{r setup, echo = FALSE}
library(knitr)

knitr::opts_chunk$set(root.dir = "../..")
# directories
datadir <- file.path(knitr::opts_chunk$get("root.dir"), "data")

cm3_jan_df <- readRDS(file.path(datadir, "model_climatology_comparison",
                                "cm3_jan_df.Rds"))
cm3_jul_df <- readRDS(file.path(datadir, "model_climatology_comparison",
                                "cm3_jul_df.Rds"))

ccsm4_jan_df <- readRDS(file.path(datadir, "model_climatology_comparison",
                                  "ccsm4_jan_df.Rds"))
ccsm4_jul_df <- readRDS(file.path(datadir, "model_climatology_comparison",
                                  "ccsm4_jul_df.Rds"))
```

##CM3 January
There is a correlation between the following quantile and mean differences of `r round(cor(cm3_jan_df$q99.00_diff, cm3_jan_df$mean_diff), 2)` for the 99.00% quantiles, and `r round(cor(cm3_jan_df$q99.90_diff, cm3_jan_df$mean_diff), 2)` for the 99.90% quantiles. 
```{r cm3_jan, echo = FALSE}
kable(cm3_jan_df)
```

##CM3 July
There is a correlation between the following quantile and mean differences of `r round(cor(cm3_jul_df$q99.00_diff, cm3_jul_df$mean_diff), 2)` for the 99.00% quantiles, and `r round(cor(cm3_jul_df$q99.90_diff, cm3_jul_df$mean_diff), 2)` for the 99.90% quantiles. 
```{r cm3_july, echo = FALSE}
kable(cm3_jul_df)
```

##CCSM4 January
There is a correlation between the following quantile and mean differences of `r round(cor(ccsm4_jan_df$q99.00_diff, ccsm4_jan_df$mean_diff), 2)` for the 99.00% quantiles, and `r round(cor(ccsm4_jan_df$q99.90_diff, ccsm4_jan_df$mean_diff), 2)` for the 99.90% quantiles. 
```{r ccsm4_jan, echo = FALSE}
kable(ccsm4_jan_df)
```

##CCSM4 July
There is a correlation between the following quantile and mean differences of `r round(cor(ccsm4_jul_df$q99.00_diff, ccsm4_jul_df$mean_diff), 2)` for the 99.00% quantiles, and `r round(cor(ccsm4_jul_df$q99.90_diff, ccsm4_jul_df$mean_diff), 2)` for the 99.90% quantiles. 
```{r ccsm4_july, echo = FALSE}
kable(ccsm4_jul_df)
```
