---
title: "AK ASOS Wind Speed Adjustment Results"
output: pdf_document
---

```{r setup, message = FALSE, warning = FALSE, echo = FALSE}
library(data.table)
library(dplyr)
library(ggplot2)
library(lubridate)

workdir <- getwd()
datadir <- file.path(workdir, "data")
figdir <- file.path(workdir, "figures")

asos_adj_path <- file.path(datadir, "AK_ASOS_daily_select_adjspeed_19800101_to_20150101.csv")
asos_adj_daily <- fread(asos_adj_path)

select_stations_path <- file.path(datadir, "select_stations.Rds")
select_stations <- readRDS(select_stations_path)
# changepoints
newfolder <- "AK_ASOS_allsites_wind_19800101_to_20150101_adj"
cpts_path <- file.path(datadir, newfolder, "cpts_df.Rds")
cpts_df <- readRDS(cpts_path)
```



Here are the monthly-averaged wind speeds for our selected sites, with changepoints significant at the 0.01 level plotted in red. The gray time series are the original unadjusted data, and the blues lines are the means of these data, segmented by the changepoints. The new, adjusted data are overlayed in black. I ommitted the black lines for stations where no significant changepoints were detected.

```{r plots, echo = FALSE, fig.height = 2, fig.width = 8, warning = FALSE, message = FALSE}
stids <- select_stations$stid
date_labels <- c("1970", "1980", "1990", "2000", "2010", "2020")
date_breaks <- as.Date(c("1970-01-01", "1980-01-01", "1990-01-01", 
                 "2000-01-01", "2010-01-01", "2020-01-01"))
theme_set(theme_bw())

for(i in 1: length(stids)){
  asos_station <- asos_adj_daily %>% filter(stid == stids[i]) %>%
    mutate(month = format(ymd(date), format = "%Y-%m"), one = 1) %>% 
    group_by(month) %>% summarise(avg_sped_mo = mean(avg_sped),
                                  avg_adj_sped_mo = mean(avg_sped_adj)) %>%
    mutate(date = as.Date(paste0(month, "-01"),
                          origin = "1970-01-01"))
  
  
  p <- ggplot(asos_station, aes(date, avg_sped_mo, group = 1)) + 
    geom_line(col = "grey") +
    xlab("") + ylab("Avg Speed (mph)") + xlim(ymd("1970-01-01"), ymd("2019-01-01")) + 
    #scale_x_date(date_labels = date_labels, breaks = date_breaks) + 
    ggtitle(stids[i]) + 
    geom_vline(xintercept = ymd("1980-01-01"), col = "gray50", lty = 3, size = 1.25) + 
    geom_vline(xintercept = ymd("2015-01-01"), col = "gray50", lty = 3, size = 1.25)
  
  
  cpts_temp <- cpts_df[cpts_df$stid == stids[i], ]
  
  if(cpts_temp[10] > 0) {
    # starting x for mean 1 line
    x1_start <- ymd("1970-01-01")
    x1_end <- cpts_temp[1, 2]
    if(cpts_temp[10] == 1) {
      x2_end <- ymd("2018-01-01")
      m1 <- cpts_temp[1, 4]
      m2 <- cpts_temp[1, 5]
      p <- p + geom_vline(xintercept = x1_end, 
                          col = "red", size = 1.5) + 
        geom_segment(aes(x = x1_start, xend = x1_end, y = m1, yend = m1),
                     col = "blue") +
        geom_segment(aes(x = x1_end, xend = x2_end, y = m2, yend = m2),
                     col = "blue") +
        geom_line(aes(date, avg_adj_sped_mo, group = 1))
    } else {
      x2_end <- cpts_temp[1, 3]
      x3_end <- ymd("2018-01-01")
      m1 <- cpts_temp[1, 4]
      m2 <- cpts_temp[1, 5]
      m3 <- cpts_temp[1, 6]

      p <- p + geom_vline(xintercept = c(x1_end, x2_end), 
                          col = "red", size = 1.5) + 
        geom_segment(aes(x = x1_start, xend = x1_end, y = m1, yend = m1),
                     col = "blue") +
        geom_segment(aes(x = x1_end, xend = x2_end, y = m2, yend = m2),
                     col = "blue") +
        geom_segment(aes(x = x2_end, xend = x3_end, y = m3, yend = m3),
                     col = "blue") +
        geom_line(aes(date, avg_adj_sped_mo, group = 1))
    }
  }
  
  print(p)
  
}

```

